Forecasting the Support of Kamala Harris in 2024 U.S. Presidential Election using a Model-Based Approach with Poll-of-Polls Data

### 2024-11-04 paper/paper.qmd
update paper

---
title: "Forecasting the Support of Kamala Harris in 2024 U.S. Presidential Election using a Model-Based Approach with Poll-of-Polls Data"
subtitle: "Kamala Harris expects to win on 47.5%, leads Donald Trump by about 1% in 2024 US election"
author: 
  - Diana Shen
  - Jinyan Wei
  - Jerry Yu
thanks: "Code and data are available at: [https://github.com/DianaShen1224/Forecast-2024-US-election](https://github.com/DianaShen1224/Forecast-2024-US-election)."
date: today
date-format: long
abstract: "This study models the 2024 U.S. Presidential Election by analyzing polling data with adjustments for factors like recency and sample size, simulating an approach that captures up-to-date voter sentiment. Using the recent 4 months of aggregated poll data, the model identifies shifts in candidate support across key battleground states, providing a nuanced view of evolving preferences as election day approaches. By emphasizing recent, high-quality polls, the analysis improves predictive reliability, offering an understanding that could inform campaign strategies and public discourse. These findings highlight the value of weighting and time-sensitive adjustments in forecasting methods, balancing accuracy with responsiveness to the latest trends."
format: pdf
toc: true
number-sections: true
bibliography: references.bib
editor: 
  markdown: 
    wrap: 72
---

@@

In this analysis, we use predictors that capture both the methodological
quality and structural aspects of each poll. Specifically, we include
variables such as `national_poll`, which reflects national support
trends; `pollster`, which represents differences in methodology and
reliability across polling organizations; and `population`, which
accounts for demographic and regional characteristics associated with
each poll. Our combined weighting approach further integrates factors
like recency and sample size to ensure that more recent, larger-sample
polls have a greater impact on the model's predictions, providing a
balanced and detailed assessment of candidate support.

@@

## Predicted Voting Outcomes for Recent Three Months by State

>>>>

---
title: "Forecasting the Support of Kamala Harris in 2024 U.S. Presidential Election using a Model-Based Approach with Poll-of-Polls Data"
subtitle: "Kamala Harris expects to win on 47.5%, leads Donald Trump by about 1% in 2024 US election"
author: 
  - Diana Shen
  - Jinyan Wei
  - Jerry Yu
thanks: "Code and data are available at: [https://github.com/DianaShen1224/Forecast-2024-US-election](https://github.com/DianaShen1224/Forecast-2024-US-election)."
date: today
date-format: long
abstract: "This study models the 2024 U.S. Presidential Election by analyzing polling data with adjustments for factors like recency and sample size, simulating an approach that captures up-to-date voter sentiment. Using the recent 4 months (July 21th - November 2th) of aggregated poll data, the model identifies shifts in candidate support across key battleground states, providing a nuanced view of evolving preferences as election day approaches. By emphasizing recent, high-quality polls, the analysis improves predictive reliability, offering an understanding that could inform campaign strategies and public discourse. These findings highlight the value of weighting and time-sensitive adjustments in forecasting methods, balancing accuracy with responsiveness to the latest trends."
format: pdf
toc: true
number-sections: true
bibliography: references.bib
editor: 
  markdown: 
    wrap: 72
---

@@

In this analysis, we use predictors that capture both the methodological
quality and structural aspects of each poll. Specifically, we include
variables such as `national_poll`, which reflects national support
trends; `pollster`, which represents differences in methodology and
reliability across polling organizations; `population`, which
accounts for the type of respondent group of voters associated with
each poll; and lastly,`state`, which represents the exact U.S. state
where the poll was conducted or focused.Our combined weighting approach further
integrates factors like recency and sample size to ensure that more recent, 
larger-sample polls have a greater impact on the model's predictions, providing a
balanced and detailed assessment of candidate support.

@@

## Predicted Voting Outcomes in Key Battleground States
